\papertitle

### 2017-02-07 paper/paper.tex
Described motivation for technique
Added power method eigenvalue computation.

\section{Introduction}
\label{sec:intro}
This template can be found on the conference website.

>>>>

\section{Introduction}
\label{sec:intro}
%Additive synthesis using a sum of sinusoids plus noise is a powerful model for
%representing audio, allowing for the easy implementation of many manipulations
%such as time-stretching and transposition. In its most basic form, peaks in the
%short-time spectrum are identified as representing sinusoids and connected based
%on some criteria. As the phase evolution of the sinusoid is assumed linear over
%the analysis frame, only the phase and frequency of the sinusoids at these
%analysis points are used to fit a plausible phase function. Recently, there has
%been interest in using higher order phase functions as the estimation of their
%parameters has been made possible by a new set of techniques of only moderate
%computational complexity using signal derivatives. Theoretically, the estimation
%of the parameters of a polynomial phase function of arbitrary order make it
%possible to approximate any analytical phase function to desired precision.
%Empirically, the use of higher order phase models allow for higher quality
%manipulations.
%
%The technique we will consider in this paper is the Distribution Derivative
%Method for its convenience: the technique does not require computing derivatives
%of the signal to be analysed. It does, however, require a
%$p$ times differentiable analysis window where $p+1$ is the order of the
%phase polynomial to be estimated.
%
%In the few reports on the technique, the window used is the Hann window. This
%window is many-times differentiable but 
%
%Complex polynomial phase models whose estimation is 
\section{The polynomial phase sinusoid}
Recently techniques estimating the parameters of polynomial phase sinusoids,
i.e., signals of the form
\[
    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
\]
have been developed. Many equivalent techniques have been developed for
estimating the $a_j$ have been developed. In this paper we compare with the
Distribution Derivative Method (DDM) only, without loss of generality.

\section{The estimation of $a_j$}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions (Laurent Schwartz), the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with respect to
$t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\]
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{equation}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df(t)}{dt} = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{equation}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df(t)}{dt}$ we obtain
%
\[
    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\]
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

\section{The estimation of the $a_{i,j}$ of $P$ components}

Although this technique can be exteded to describe a single
sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
interest to consider a signals featuring a sum of such components, i.e.,
%
\[
    s(t) = \sum_( \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j) )
\]
%
In situations where multiple signal sources are known to exist (e.g., recordings
of multiple speakers or performers) such a model is plausible.

We examine how this mixture model influences the estimation of the $a_{i,j}$.
Consider a mixture of $P$ components
%
\[
    s(t) = \sum_{i=1}{P} x_{i}(t)
\]
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in \ref{eq:ddm:weighted:sig:derivative} we obtain
%
\[
    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0 = 
    \sum_{i=1}{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ is small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_i, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$.

\section{Designing the \psi_{r}}

In practice, an approximation of \ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \frac{1}{N} \sum_{n=0}{N-1} x(Tn) w(Tn) exp(-2 \pi j r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $\frac{L_{t}}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%

The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies $\frac{r}{N}$ and with frequency response described by
the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter must be differentiable in $t$ and finite.

In all the publications these authors reviewed on the DDM, the window used was
the Hann window.
Nuttall has designed windows with greater out-of-band rejection (lower
side-lobes) than the canonical Hann window which are still differentiable.
